Geometric Filters for Metric Spaces

### 2018-11-26 paper/draft.tex
interim

\begin{algorithmic}
\Function{DiscardPoints}{$L, p_i, r_i, \eps$}
    \ForAll { $p_j \in L$}
       \If { $ \dist(p_i, p_j) < r_j - r_i / ( 1 + \eps) $ }
           \State {Remove $p_j$ from $L$}
       \EndIf

       \If {  $ \dist(p_i, p_j) > r_j + r_i / ( 1 + \eps) $ }
           \State {Remove $p_j$ from $L$}
       \EndIf

    \EndFor
\EndFunction
\end{algorithmic}

\begin{algorithmic}
\Function{ApproximateNearestNeighbor}{$P, q, \eps$}
    \State {Initialize list $L$ with a random permutation of $P$}
    \While {$L$ is not empty}
        \State {Set current candidate $p_i$ to be the first element of $L$}
        \State {Compute $r_i = \dist(q, p_i)$}
        \State \Call{DiscardPoints}{$L, p_i, r_i, \eps$}
        \ForAll {$p_j \in L $}
            \State {Compute $r_j = \dist(p_j, q)$}
            \State \Call{DiscardPoints}{$L, p_j, r_j$}
        \EndFor
    \EndWhile
\EndFunction
\end{algorithmic}

\begin{algorithmic}
\Function{ApproximateNearestNeighbor}{$P, q, \eps$}
\For {$i \in \{\,1, \dots, |P|\,\}$}
\State {$a_i \gets 0$}
\State {$b_i \gets \infty$}
\EndFor
%\State {$i_0 \gets \argmin u $}
\State {$B  \gets \{\, i \mid l_i < u[i_0]\,\}$}
\If {$B = \emptyset$}
    \State {\Return {$p_{i_0}$}}
\Else
    \State{$j \gets \mbox{ random element of } C$}
    \State{$u_j \gets d(p_j, q)$}
    \State{$l[j] \gets d(p_j, q)$}
    \State{Mark distance from $q$ to $p_j$ as computed}
    \State{\Call{UpdateBounds}{$l, u, d(p_j, q), j$}}
\EndIf
\EndFunction
\end{algorithmic}

>>>>

\begin{algorithmic}
\Procedure{Discard\_1}{$L, p_i$}
    \State {$r_i = \dist(q, p_i)$}
    \ForAll { $p_j \in L$}
       \If {  $ \dist(p_i, p_j) > r_i \left(1 + \frac{1}{ 1 + \eps} \right)$ }
           \State {Remove $p_j$ from $L$}
       \EndIf
    \EndFor
\EndProcedure
\end{algorithmic}

\begin{algorithmic}
\Procedure{Discard\_2}{$L, w, c$}
    \State {$r_w = \dist(q, w)$}
    \State {$r_c = \dist(q, w)$}
    \Comment {Distances $r_w$ and $r_c$ are cached}
    \ForAll { $p_j \in L$}
       \If { $ \dist(w, p_j) < r_w - r_c / ( 1 + \eps) $ }
           \State {Remove $p_j$ from $L$}
           \Comment {In particular, the worse candidate $w$ will be removed here}
       \EndIf
       \If {  $ \dist(w, p_j) > r_w + r_c / ( 1 + \eps) $ }
           \State {Remove $p_j$ from $L$}
       \EndIf
    \EndFor
\EndProcedure
\end{algorithmic}

\begin{algorithmic}
\label{alg:ann_blind}
\Function{ApproximateNearestNeighbor}{$P, q, \eps$}
    \State {Initialize array $L$ with a random permutation of $P$}
    \State {$ c \gets \mbox{the first element of }L$}
    \State {Compute $r_i = \dist(q, p_i)$}
    \While {$|L| > 1$}
        \State \Call{Discard\_1}{$L, c$}
        \ForAll {$p_j \in L $}
            \State {Compute $r_j = \dist(p_j, q)$}
            \Comment {Set the worse candidate $w$ to be either $p_i$ or $p_j$}
            \If {$r_j < r_i$ }
                \State {$ c \gets p_j $}
                \State {$ w \gets p_i $}
            \Else
                \State {$ w \gets p_i $}
            \EndIf
            \State \Call{Discard\_2}{$L, w, c$}
        \EndFor
    \EndWhile
    \State \Return {the unique element left in $L$}
\EndFunction
\end{algorithmic}
